An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/learner.tex
config: learner

The goal of the learner module is to derive rules and constraints from
the intermediate representation generated by the translator.
It has two components.
The first component ($\S$\ref{subsec-rules}) 
learns rules for checking misconfiguration errors like
missing entry, ordering, and fine-grained value correlation errors. 
These errors tend to cause total system failures.
%Once the configuration file has been validated against such rules, 
%the user may choose to invoke a more sensitive constraint checker. 
The second component ($\S$\ref{subsec-constraints}) 
aims to derive 
constraints on entries to check for suspicious (or anomalous) values 
that may violate standard practice. These anomalies can cause partial 
degradation of the system, such as significant reduction in performance, or even 
total failure as in Example~4 of $\S$\ref{sec-motiv}.

@@

>>>>

The goal of the learner module is to derive rules and constraints from
the intermediate representation generated by the translator.
In general, the learner module has two components.
The first component ($\S$\ref{subsec-rules}) 
learns rules for checking configuration errors like
entry missing, ordering errors, and fine-grained value correlation errors. 
These errors tend to cause total system failures.
%Once the configuration file has been validated against such rules, 
%the user may choose to invoke a more sensitive constraint checker. 
The second component ($\S$\ref{subsec-constraints}) 
aims to derive 
constraints on entries to check for suspicious (or anomalous) values 
that may violate standard practice. These anomalies can cause partial 
degradation of the system, 
such as significant reduction in performance, or even 
total failure as in Example~4 of $\S$\ref{sec-motiv}.

@@

\ennan{So far, it is still not clear what does 
our claimed language model look like?}
